Capstone Movielens Report

### 2025-12-15 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame representing the _RMSEs Result Tibble_ to store the _RMSE_ values for every model used in the project to predict movie ratings.

@@

This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.

@@

This function is a wrapper for the [tibble::add_column](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_column) function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_. It also internally uses the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above to perform the necessary intermediate calculations.

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_effect.args.lambda) arg value other than default) *UM Effect Model*.
:::

@@

Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.calc_user_movie_effect_MSE.args.um_effect .sidebar }
  - **um_effect:** Data frame representing the *UM Effect Model*.

@@

::: { #func.calc_user_movie_effect_MSE.cv.args.um_effect .sidebar }
  - **um_effect:** Data frame representing the *UM Effect Model*.

@@

::: { #func.calc_user_movie_effect_RMSE.cv.args.um_effect .sidebar }
  - **um_effect:** Data frame representing the *UM Effect Model*.

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UMG Effect Model*.
:::

@@

Under the hood, this function internally calls the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.calc_user_movie_genre_effect_MSE.args.umg_effect .sidebar }
  - **umg_effect:** Data frame representing the *UMG Effect Model*.

@@

::: { #func.calc_user_movie_genre_effect_MSE.cv.args.umg_effect .sidebar }
  - **umg_effect:** Data frame representing the *UMG Effect Model*.

@@

::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.umg_effect .sidebar }
  - **umg_effect:** Data frame representing the *UMG Effect Model*.

@@

Data frame representing (*regularized* if [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
:::

@@

Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Data frame representing (*regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
:::

@@

::: { #func.calc_UMGY_effect.args.date_general_effect .sidebar }
  - **date_general_effect:** Data frame representing the *Date General Effect*;

@@

Data frame representing the *UMGYE Model*.
:::

@@

Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
:::

@@

Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.calc_UMGY_effect_MSE.args.UMGY_effect .sidebar }
  - **UMGY_effect:** Data frame representing the *UMGY Effect Model*.

@@

::: { #func.calc_UMGY_effect_MSE.cv.args.UMGY_effect .sidebar }
  - **UMGY_effect:** Dataframe object representing the *UMGY Effect Model*.

@@

::: { #func.calc_UMGY_effect_RMSE.cv.args.UMGY_effect .sidebar }
  - **UMGY_effect:** Data frame representing the *UMGY Effect Model*.

@@

Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *DG Effect*.
:::

@@

Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Day General Effect*.
:::

@@

Dataframe object representing the *Day General Effect* data.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
  - **date_general_effect:** Dataframe object representing the *DG Effect* (to pass in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument to the internally called [loess_de](#func.loess_de) described above);

@@

Data frame representing the *UMGYDE Model*.
:::

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
:::

@@

Dataframe representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.

@@

Dataframe object containing *predicted user rating* values based on the *UMGYDE Model*
:::

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.

@@

Trains and validate (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the given parameter values passed in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) arguments, with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.

@@

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument and the `degree` parameter equals $0$.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

@@

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $1$.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $1$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

@@

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $2$.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $2$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

@@

Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.

@@

@@

:::
::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

::: {.noteblock data-latex=""}
The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
:::
:::

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
:::

@@

The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
```{r eval=FALSE}
```

@@

Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

@@

::: {.noteblock data-latex=""}
In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below, along with the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above in this section.
:::
:::

>>>>

This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame object representing the _RMSEs Result Tibble_ to store the _RMSE_ values for every model used in the project to predict movie ratings.

@@

This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame object representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.

@@

This function is a wrapper for the [tibble::add_column](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_column) function, which is called internally to modify a data frame object representing the original _RMSEs Result Tibble_. It also internally uses the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above to perform the necessary intermediate calculations.

@@

Data frame object representing the trained (and also *regularized* if [lambda](#func.train_user_movie_effect.args.lambda) arg value other than default) *UM Effect Model*.
:::

@@

Internally, this function calls the helper function [train_user_movie_effect](#func.train_user_movie_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Data frame object representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.calc_user_movie_effect_MSE.args.um_effect .sidebar }
  - **um_effect:** Data frame object representing the *UM Effect Model*.

@@

::: { #func.calc_user_movie_effect_MSE.cv.args.um_effect .sidebar }
  - **um_effect:** Data frame object representing the *UM Effect Model*.

@@

::: { #func.calc_user_movie_effect_RMSE.cv.args.um_effect .sidebar }
  - **um_effect:** Data frame object representing the *UM Effect Model*.

@@

Data frame object representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UMG Effect Model*.
:::

@@

Internally, this function calls the helper function [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Data frame object representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.calc_user_movie_genre_effect_MSE.args.umg_effect .sidebar }
  - **umg_effect:** Data frame object representing the *UMG Effect Model*.

@@

::: { #func.calc_user_movie_genre_effect_MSE.cv.args.umg_effect .sidebar }
  - **umg_effect:** Data frame object representing the *UMG Effect Model*.

@@

::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.umg_effect .sidebar }
  - **umg_effect:** Data frame object representing the *UMG Effect Model*.

@@

Data frame object representing (*regularized* if [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
:::

@@

Internally, this function calls the helper function [calc_date_general_effect](#func.calc_date_general_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Data frame object representing (*regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
:::

@@

::: { #func.calc_UMGY_effect.args.date_general_effect .sidebar }
  - **date_general_effect:** Data frame object representing the *Date General Effect*;

@@

Data frame object representing the *UMGYE Model*.
:::

@@

Internally, this function calls the helper functions [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) (both described above in this section).

@@

Data frame object representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
:::

@@

Internally, this function calls the helper functions [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) (both described above in this section).

@@

Data frame object representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.calc_UMGY_effect_MSE.args.UMGY_effect .sidebar }
  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.

@@

::: { #func.calc_UMGY_effect_MSE.cv.args.UMGY_effect .sidebar }
  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.

@@

::: { #func.calc_UMGY_effect_RMSE.cv.args.UMGY_effect .sidebar }
  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.

@@

Data frame object representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *DG Effect*.
:::

@@

Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

@@

Data frame object representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Day General Effect*.
:::

@@

Data frame object representing the *Day General Effect* data.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
  - **date_general_effect:** Data frame object representing the *DG Effect* (to pass in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument to the internally called [loess_de](#func.loess_de) described above);

@@

Data frame object representing the *UMGYDE Model*.
:::

@@

Data frame object representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
:::

@@

Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.

@@

Data frame object containing *predicted user rating* values based on the *UMGYDE Model*
:::

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.

@@

Trains and validate (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the given [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters passed in the corresponding arguments ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span)), with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
  - **degree:** (Integer, `NA` by default) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.

@@

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument and the `degree` parameter equals $0$.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :

  - $0$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;

  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).

@@

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $1$.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :

  - $1$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;

  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).

@@

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $2$.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :

  - $2$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;

  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).

@@

Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for a given value of the parameter $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument and preliminary figured out *best values* of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters, using the training set of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.

@@

```{r eval=FALSE}
  rglr.UMGYD_effect <- edx |> 
    regularize.train_UMGYD_effect(UMGYDE.rglr.best_lambda)
```
:::

@@

:::
::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
  - **lambda:** Regularization parameter $\lambda$.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*) that it calls internally, passing it the best values of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters `degree` and `span` in the corresponding arguments ([degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span), respectively)

::: {.noteblock data-latex=""}
The *UMGYDE Model* is regularized using the *regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
:::
:::

@@

Data frame object representing the *UMGYDE Model*, regularized by the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument) and tuned for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) *best parameters* `degree` and `span`.
:::

@@

The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
```{r eval=FALSE}
regularize.train_UMGYD_effect <- function(train_set, lambda) {
  best_degree <- lss.UMGYDE.best_params["degree"]
  best_span <- lss.UMGYDE.best_params["span"]

  train_set |>
    train_UMGY_SmoothedDay_effect(best_degree, 
                                  best_span, 
                                  lambda)
}
```

@@

Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for a given value of the parameter $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument and preliminary figured out *best values* of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters, with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

@@

```{r eval=FALSE}
  regularize.train_UMGYD_effect.cv(lambda) |>
    calc_UMGY_SmoothedDay_effect.RMSE.cv()
```

::: {.noteblock data-latex=""}
In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in this section, along with the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above in section [UMGYDE Model: Utility Functions].
:::
:::
